---
title: "Statistical Inference Course Project"
author: "Humbert Costas"
date: "22 de agosto de 2015"
output: html_document
---

# Overview
In this project I will **investigate the exponential distribution** in R **and compare it with the Central Limit Theorem**. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. I will ***set lambda = 0.2*** for all of the simulations. I will investigate the distribution of averages of 40 exponentials.

```{r overview}
set.seed(666)   # Reproducibility purposes
n <- 40         # Number of samples
lambda <- .2     # Set lambda to 0.2
nsims <- 1000   # Number of simulations
```

## Simulations
Illustration via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponentials.

```{r simulations}
sam = NULL
for (i in 1:1000) sam = c(sam, rexp(n,lambda))

# Mean and Variabce of the exponential distributions
s_means <- apply(sam,2,mean)
s_mean <- mean(s_means)
s_sd <- sd(sam)^2
s_var <- var(sam)

# Theoretical Mean and Variance
t_mean <- 1 / lambda
t_sd <- ((1 / lambda) ^ 2) / n
t_var <- t_sd ^ 2
```


1. Show the sample mean and compare it to the theoretical mean of the distribution.
2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
3. Show that the distribution is approximately normal.
