---
title: "Statistical Inference Course Project 2"
author: "Humbert Costas"
date: "22 de agosto de 2015"
output: html_document
---

## Overview
Now in the second portion of the class, we're going to analyze the ToothGrowth data in the R datasets package.

1. Load the ToothGrowth data and perform some basic exploratory data analyses

Data shows the results of a study on the effects that Vitamic C has on the growth (length) of teeth of guinea pigs. Vitamin C was provided either in the form of Orange Juice (OJ) or ascorbic acid (VC), at three different dose levels to 10 animals, giving a total of 60 different sample values.
```{r exploratory}
data(ToothGrowth)
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
str(ToothGrowth)
summary(ToothGrowth)
```
2. Provide a basic summary of the data.
Let's take a look of the data distribution with a scattered point graph 
```{r summary}
library(ggplot2)
g <- ggplot(ToothGrowth, aes(x = dose,y = len, color = supp))
g <- g + geom_point(alpha = 0.5, size = 5)
g <- g + ylab("Lenght of Teeth")
g <- g + xlab("Dose (mg)")
g <- g + ggtitle("Tooth growth on guinean Pigs")
print(g)
```

3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
4. State your conclusions and the assumptions needed for your conclusions. 
Some criteria that you will be evaluated on
 - Did you  perform an exploratory data analysis of at least a single plot or table highlighting basic features of the data?
 - Did the student perform some relevant confidence intervals and/or tests?
 - Were the results of the tests and/or intervals interpreted in the context of the problem correctly? 
 - Did the student describe the assumptions needed for their conclusions?
